Week 5 R Quiz
========================================================

**1. Create the following five matrices in R:**

```{r echo=TRUE}
A <- matrix(c(1,-1,-1,-1),ncol=2,nrow=2)
B <- matrix(c(2,-1,3,-2),ncol=2,nrow=2)
C <- matrix(c(1,0,0,0),ncol=2,nrow=2)
D <- matrix(c(0,1,0,1,0,0,0,0,1),ncol=3,nrow=3)
E <- matrix(c(1,0,0,0,0,1,0,1,0),ncol=3,nrow=3)

A
B
C
D
E
```

**2. Research the definition of an idempotent matrix. Use the appropriate matrix multiplication techniques in R to determine which of the five matrices above are idempotent.**

Matrices are idempotent if the product of the matrix and itself are equal to the original matrix (A = A*A).


```{r echo=TRUE}
A2 <- A %*% A
B2 <- B %*% B
C2 <- C %*% C
D2 <- D %*% D
E2 <- E %*% E

## Compare A to A*A. If the two are equal, A is an idempotent matrix.
identical(A,A2)

## Compare B to B*B. If the two are equal, B is an idempotent matrix.
identical(B,B2)

## Compare C to C*C. If the two are equal, C is an idempotent matrix.
identical(C,C2)

## Compare D to D*D. If the two are equal, D is an idempotent matrix.
identical(D,D2)

## Compare E to E*E. If the two are equal, E is an idempotent matrix.
identical(E,E2)
```

C, D and E are idempotent.

**3. Research the definition of an orthogonal matrix. Use the appropriate matrix multiplication techniques in R to determine which of the five matrices above are orthogonal.**

Matrices are orthogonal if the product of the matrix and the matrix transposed equal an identity matrix (A * A^t = I).

``` {r echo=TRUE}
## Create identity matrices.
I2 <- matrix(c(1,0,0,1),nrow=2)
I3 <- matrix(c(1,0,0,0,1,0,0,0,1),nrow=3)

A3 <- A * t(A)
B3 <- B * t(B)
C3 <- C * t(C)
D3 <- D * t(D)
E3 <- E * t(E)

## Compare A3 to I2. If the two are equal, A is an orthogonal matrix.
identical(A3,I2)

## Compare B3 to I2. If the two are equal, B is an orthogonal matrix.
identical(B3,I2)

## Compare C3 to I2. If the two are equal, C is an orthogonal matrix.
identical(C3,I2)

## Compare D3 to I3. If the two are equal, D is an orthogonal matrix.
identical(D3,I3)

## Compare E3 to I3. If the two are equal, E is an orthogonal matrix.
identical(E3,I3)

```

None of these matrices are orthogonal.

**4. Illustrate the creation of a list that contains a vector, a matrix, an array, a dataframe, and another list. (You may use one of the matrices above if you wish to do so. You'll need to create the other items yourself.)**

```{r echo=TRUE}

myList = list("vector",A,array(1:6),data.frame(),list(1,2,3));
myList

```