Week 8 - R Quiz
========================================================

**1. Illustrate how to add element by element the contents of two numeric vectors of equal length using a for loop. Comment on how this differs from the easier vector addition method preferred in R.**

```{r}
v1 <- floor(rnorm(10,12,2))
v2 <- floor(rnorm(10,12,2))

newVector <- c()
  
if(length(v1)==length(v2)) {
  for(i in 1:length(v1)) {
    newVector[i]<-v1[i]+v2[i]
  }
}

newVector

```

Adding vectors element by element using a for loop is significantly more complicated than the simple vector addition method available in R:

```{r}
v1 <- floor(rnorm(10,12,2))
v2 <- floor(rnorm(10,12,2))

newVector <- v1+v2
newVector

```

**2. Write code that uses a while loop that determines how many "heads" in a row an arbitrary vector of coin flips has starting at the beginning. An example of a vector input is c("heads","heads","tails","heads"). Your code should give an answer of 2 when run on this vector. Note that a vector that begins with "tails" should give an answer of 0.**

```{r}
v3 <- c("heads","heads","tails","heads")

last <- "heads"
count <- 0
index <- 1

while(last=="heads") {
  if(index < length(v3)) {
    if(v3[index]=="heads") {
      count <- count + 1
      index <- index + 1
    } else {
      last <- "tails"
    } 
  }
}
count
```

**3. Use a for loop running over all 100 integers from 1 to 100 and the ifelse() function to add only the odd numbers from 1 to 100. BONUS: Can you show how to accomplish the same thing without using a loop?**

```{r}
ints <- c(1:100)
total <- 0
for(i in ints) {
  total <- ifelse(i %% 2 == 0, total + i, total) 
}
total
```
